Responsible Machine Learning Techniques\\\large{Interpretable Models, Post-hoc Explanation, and Discrimination Testing}

### 2019-12-13 article-information-2019.tex
some progress on figures

\begin{table}[H]
\label{tab:sim_acc}
\caption{Accuracy metrics for $g^\text{GBM}$, $g^\text{MGBM}$, $g^\text{ANN}$, and $g^\text{XNN}$ on the simulated test data.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccccc}
\toprule
\textbf{Model}		& \textbf{Accuracy}	& \textbf{AUC}	 & \textbf{Logloss}	& \textbf{RMSE}\\
\midrule
$g^\text{GBM}$		& 0.775	& 0.857	& 0.474	& 0.394 \\
$g^\text{MGBM}$	& 0.763	& 0.846	& 0.498	& 0.405 \\
$g^\text{ANN}$		& 		& 			& 				& \\
$g^\text{XNN}$		& 		& 			& 				& \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\label{tab:mort_acc}
\caption{Accuracy metrics for $g^\text{GBM}$, $g^\text{MGBM}$, $g^\text{ANN}$, and $g^\text{XNN}$ on the mortgage test data.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccccc}
\toprule
\textbf{Model}		& \textbf{Accuracy}	& \textbf{AUC}	 & \textbf{Logloss}	& \textbf{RMSE}\\
\midrule	
$g^\text{GBM}$		& 0.795	& 0.828	& 0.252	& 0.276 \\
$g^\text{MGBM}$	& 0.765	& 0.814	& 0.259	& 0.278 \\
$g^\text{ANN}$		& 		& 		& 		& \\
$g^\text{XNN}$		& 		& 0.868	& 0.233	& 0.263 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[H]
\centering
%\includegraphics[width=8cm]{img/}
\label{fig:mort_mgbm_glob}
\caption{Global mean Tree SHAP feature importance for $g^\text{MGBM}$ on the mortgage test data.}
\end{figure}

\begin{figure}[H]
\centering
%\includegraphics[width=8cm]{img/}
\label{fig:mort_mgbm_glob_pdp_ice}
\caption{PD, ICE across deciles, and histograms for the three most important input features for $g^\text{MGBM}$ on the mortgage test data.}
\end{figure}

@@

\begin{figure}[H]
\centering
%\includegraphics[width=8cm]{img/}
\label{fig:mort_mgbm_loc}
\caption{Mean Tree SHAP values across quintiles for the three most important input features for $g^\text{MGBM}$ on the mortgage test data.}
\end{figure}

\begin{figure}[H]
\centering
%\includegraphics[width=8cm]{img/}
\label{fig:mort_xnn_glob}
\caption{Global mean Deep SHAP feature importance for $g^\text{XNN}$ on the mortgage test data.}
\end{figure}

>>>>

\begin{table}[H]
\label{tab:sim_acc}
\caption{Fit metrics for $g^\text{GBM}$, $g^\text{MGBM}$, $g^\text{ANN}$, and $g^\text{XNN}$ on the simulated test data. Accuracy is measured at the best F1 threshold for each model.}
\centering
\begin{tabular}{ccccc}
\toprule
\textbf{Model}		& \textbf{Accuracy}	& \textbf{AUC}	 & \textbf{Logloss}	& \textbf{RMSE}\\
\midrule
$g^\text{GBM}$		& 0.775	& 0.857	& 0.474	& 0.394 \\
$g^\text{MGBM}$	& 0.763	& 0.846	& 0.498	& 0.405 \\
$g^\text{ANN}$		& 		& 		& 		& \\
$g^\text{XNN}$		& 0.758	& 0.851	& 0.479	& 0.397 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\label{tab:mort_acc}
\caption{Fit metrics for $g^\text{GBM}$, $g^\text{MGBM}$, $g^\text{ANN}$, and $g^\text{XNN}$ on the mortgage test data. Accuracy is measured at the best F1 threshold for each model.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccccc}
\toprule
\textbf{Model}		& \textbf{Accuracy}	& \textbf{AUC}	 & \textbf{Logloss}	& \textbf{RMSE}\\
\midrule	
$g^\text{GBM}$		& 0.795	& 0.828	& 0.252	& 0.276 \\
$g^\text{MGBM}$	& 0.765	& 0.814	& 0.259	& 0.278 \\
$g^\text{ANN}$		& 		& 		& 		& \\
$g^\text{XNN}$		& 0.869	& 0.868	& 0.233	& 0.263 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=8cm]{img/mort_mgbm_glob.png}
\label{fig:mort_mgbm_glob}
\caption{Global mean absolute Tree SHAP feature importance for $g^\text{MGBM}$ on the mortgage test data. Tree SHAP values are reported in the margin space, prior to the application of the logit link function.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=15cm]{img/mort_mgbm_glob_pdp_ice.png}
\label{fig:mort_mgbm_glob_pdp_ice}
\caption{PD, ICE across selected percentiles, and histograms for the three most important input features for $g^\text{MGBM}$ on the mortgage test data.}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=15cm]{img/mort_mgbm_loc.png}
\label{fig:mort_mgbm_loc}
\caption{Mean Tree SHAP values across quintiles for the three most important input features for $g^\text{MGBM}$ on the mortgage test data.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=8cm]{img/mort_xnn_glob.png}
\label{fig:mort_xnn_glob}
\caption{Global mean absolute Deep SHAP feature importance for $g^\text{XNN}$ on the mortgage test data. Deep SHAP values are reported in the probability space, after the application of the logit link function.}
\end{figure}
